Water Management

### 2020-02-22 Paper/paper.tex
write figur in capital
add todo
fix todos

% TODO delete the lorem ipsum
\usepackage{blindtext} % Package to generate dummy text throughout this template

@@

Now, it's trivial to compute the flow at any given time using code, simply by implementing the formula as given above. 
However, if we want to compute the amount of water flowing through the pipe in the time interval $[0.25, 0.5]$, we can not calculate that directly, as we would have to know the antiderivative of $f(t)$. 
Apart from this example, it's not always trivial to calculate the antiderivative of a function analytically. 
[TODO: zwei mal however]However it is possible compute the area below (almost) any function using numerical integration, also called numerical quadrature.

@@

where $u(s,x)$ is the utility to gain from the control variable (action) $x$ in state $s$ [TODO: QUOTE Seminar Week 3].

@@

% Finally, we want to compute the value of the steady state by using a monte carlo simulation. 
% TODO: hier steady state und monte carlo simulation erklären oder besser in results?

@@

% TODO maybe move to theory?

@@

To analyze it nevertheless, we defined our steady state, to be a state, where the mean water level of the last 200 periods did not change more than $1x10^{-7}$ from a period to the next.

@@

\ref{fig:rainfall-real-data} shows the distribution of rain from a real data set. %TODO "figure" -> "Figure" groß schreiben!

@@

\printbibliography

@@

%----------------------------------------------------------------------------------------
%	STATUTORY DECLARATION IN LIEU OF AN OATH
%----------------------------------------------------------------------------------------

\begingroup
\begin{center}
	\large
	\textbf{Eidesstattliche Versicherung}
\end{center}

@@

\begin{tabular}{@{}p{8cm}p{5.8cm}}
	\underline{\hspace{6cm}} & \underline{\hspace{5.8cm}} \\
	\vspace{0.02cm}Name, Vorname & \vspace{0.02cm}Matrikelnummer \\
\end{tabular}
\vspace{0.3cm}

@@

\begin{tabular}{@{}p{8cm}p{5.8cm}}
	\underline{\smash{Aachen, den \today}} & \underline{\hspace{5.8cm}}\\
	Ort, Datum & Unterschrift \\
\end{tabular}

@@

\begin{tabular}{@{}p{8cm}p{5.8cm}}
	\underline{\smash{Aachen, den \today}} & \underline{\hspace{5.8cm}}\\
	Ort, Datum & Unterschrift \\
\end{tabular}

>>>>

@@

Now, it's trivial to compute the flow at any given time using code, simply by implementing the formula as given above. 
However, if we want to compute the amount of water flowing through the pipe in the time interval $[0.25, 0.5]$, we can not calculate that directly, as we would have to know the antiderivative of $f(t)$. 
Apart from this example, it's not always trivial to calculate the antiderivative of a function analytically. 
Nonetheless it is possible compute the area below (almost) any function using numerical integration, also called numerical quadrature.

@@

where $u(s,x)$ is the utility to gain from the control variable (action) $x$ in state $s$ %TODO: QUOTE Seminar Week 3.

@@

% Finally, we want to compute the value of the steady state by using a monte carlo simulation.

@@

@@

To analyze it nevertheless, we defined our steady state, to be a state, where the mean water level of the last 200 periods did not change more than $1*10^{-7}$ from a period to the next.

@@

%TODO update figures
Figure \origref{fig:rainfall-real-data} shows the distribution of rain from a real data set.

@@

\section{Conclusion}
%TODO content
\printbibliography

@@

%----------------------------------------------------------------------------------------
%	STATUTORY DECLARATION IN LIEU OF AN OATH
%----------------------------------------------------------------------------------------
\pagestyle{empty} 
\begingroup
\begin{center}
	\large
	\textbf{Eidesstattliche Versicherung}
\end{center}

@@

\begin{tabular}{@{}p{8cm}p{5.8cm}}
	\underline{\hspace{6cm}} & \underline{\hspace{5.8cm}} \\
	\vspace{0.02cm}Name, Vorname & \vspace{0.02cm}Matrikelnummer \\
	&\\
	\underline{\hspace{6cm}} & \underline{\hspace{5.8cm}} \\
	\vspace{0.02cm}Name, Vorname & \vspace{0.02cm}Matrikelnummer \\
	&\\
	\underline{\hspace{6cm}} & \underline{\hspace{5.8cm}} \\
	\vspace{0.02cm}Name, Vorname & \vspace{0.02cm}Matrikelnummer \\
\end{tabular}
\vspace{0.3cm}

@@

\begin{tabular}{@{}p{8cm}p{5.8cm}}
	\underline{\smash{Aachen, den \hspace{4cm}}} & \underline{\hspace{5.8cm}}\\
	Ort, Datum & Unterschrift \\
	&\\
	\underline{\smash{Aachen, den \hspace{4cm}}} & \underline{\hspace{5.8cm}}\\
	Ort, Datum & Unterschrift \\
	&\\
	\underline{\smash{Aachen, den \hspace{4cm}}} & \underline{\hspace{5.8cm}}\\
	Ort, Datum & Unterschrift \\
\end{tabular}

@@

\vspace{0.6cm}
\begin{tabular}{@{}p{8cm}p{5.8cm}}
	\underline{\smash{Aachen, den \hspace{4cm}}} & \underline{\hspace{5.8cm}}\\
	Ort, Datum & Unterschrift \\
	&\\
	\underline{\smash{Aachen, den \hspace{4cm}}} & \underline{\hspace{5.8cm}}\\
	Ort, Datum & Unterschrift \\
	&\\
	\underline{\smash{Aachen, den \hspace{4cm}}} & \underline{\hspace{5.8cm}}\\
	Ort, Datum & Unterschrift \\
\end{tabular}
